% !TEX root = master_thesis.tex
\chapter{Event selection}
The determination of polarization observables needs to be completed for particular reactions (cf. chapter \ref{chap:intro}), such as the photoproduction of e.g. a single $\eta'$ meson. However, the recorded events  contain data from the decay products of all possible final states in addition to combinatorical background. Thus, event candidates for the desired reaction have to be extracted before they are considered for further analysis. Table \ref{tab:etap} shows the five most probable decay modes of the $\eta'$ meson. Three of these result in final states which only contain photons and are thus accessible for reliable measuring with the CBELSA/TAPS experiment. Only the $\eta'\to\gamma\gamma$ decay channel was considered for further analysis; the $\omega\gamma$ channel provides negligible statistics and considering the acceptance of detecting six photons in the final state, the expected yield of the $\eta'\to\gamma\gamma$ decays should be roughly equal to the $\eta'\to\pi^0\pi^0\eta\to6\gamma$ final state \cite{farah}. Offering a cleaner, three-particle final state, the $\eta'\to\gamma\gamma$ was then favored in the course of this thesis.      
\begin{table}[htbp]
	\centering
	\begin{tabular}{cc}
		\toprule
		Decay mode&Branching ratio\\
		\hline
		$\pi^+\pi^-\eta$&42.6\%\\
		$\rho^0\gamma(\pi^+\pi^-\gamma)$ &28.9\% (28.9\%)\\
	$\pi^0\pi^0\eta(6\gamma)$ & 22.8\% (8.8\%)\\
		$\omega\gamma (\pi^+\pi^-\pi^0\gamma/\pi^0\gamma\gamma)$&2.52\% (2.2\%/0.21\%)\\
	$\gamma\gamma$&2.3\%\\

		\bottomrule
	\end{tabular}
\caption{The five most probable decay modes of the $\eta'$ meson. The most probable further decay with according branching ratio is shown in brackets.\cite{pdg}}
\label{tab:etap}
\end{table}



The process of \emph{event selection} for the reaction $\gamma p \to p\eta'\to p\gamma\gamma$ is outlined in the following chapter.

    

\section{Time of particles}