%------------------------------------------------------------------------------
\chapter*{Acknowledgements}
\label{sec:ack}
%------------------------------------------------------------------------------

\noindent First of all I would like to thank \textsc{Annika Thiel} for giving me the opportunity of being part of her research group since the beginning of my bachelor thesis in 2020. Now, with the formulation of this thesis, I will be finishing my academic career in Bonn. I greatly appreciate the insight into research I could gain.
\vspace{1cm}

\noindent I express my thanks to \textsc{Reinhard Beck} who agreed to be the second referee for this thesis.
\vspace{1cm}

\noindent This thesis could not have been written without the help of \textsc{Farah Afzal}. After all, it was you, who got me into the boat again after my bachelor thesis. Over the past year we have shared our office and many fruitful discussions regarding physics (or not) were had. I am thankful that you and your masters and PhD thesis provided such excellent foundation for me to rely my work on.
\vspace{1cm}

\noindent Being the pioneer of the working group \textsc{Beck/Thiel} in all things regarding \textsc{Bayesian} statistics, \textsc{Philipp Krönert} contributed the idea of what shall fill about half of this thesis and furthermore his help and guidance whenever i got stuck on the way. I am grateful that we were able to turn the thesis into this direction with your help.
\vspace{1cm}

\noindent Also, I express my gratitude to everybody who was included in the process of data taking, i.e. the CBELSA/TAPS collaboration and crew. No analysis could have been performed without the data.
\vspace{1cm}

\noindent I thank \textsc{Farah Afzal, Philipp Krönert, Dominic Schüchter} and \textsc{Nikolas Pässler} for reading my thesis and providing me with useful comments and insights.
\vspace{1cm}

\noindent Finally, I thank my parents, for the (financial) support throughout my whole studies, which now then officially come to an end. 

   


%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../mythesis"
%%% End: 
